HPC--101\\Onboarding

### 2020-01-17 hpc_101/sections/04_security.tex
addition of more secruity slides

\begin{frame}
  \frametitle{What is data governance}
  %        \begin{definition}\footnotesize
  %          Data governance is a data management concept concerning the capability that enables an organization to ensure that high data quality exists throughout the complete lifecycle of the data. The key focus areas of data governance include availability, usability, consistency, data integrity and data security and includes establishing processes to ensure effective data management throughout the enterprise such as accountability for the adverse effects of poor data quality and ensuring that the data which an enterprise has can be used by the entire organization.
  %        \footnote[1,frame]{\tiny \href{https://en.wikipedia.org/wiki/Data\_governance}{https://en.wikipedia.org/wiki/Data\_governance}}
  %        \end{definition}
  \begin{itemize}
  \item Defines how data are collected, stored, and used
  \item Defines who can access data, when, and under what conditions
  \item Establishes decision rights
  \item Establishes clear lines of accountability
  \item Gives a voice to all appropriate parties
  \item Provides a mechanism for conflict resolutions involving data
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Data Classifications @ UH}
  \begin{table}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||p{6cm}||p{6cm}}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
	\toprule                                                                    
        \thead{\large\textbf{Category}} & \thead{\large\textbf{Definition}} & \thead{\large\textbf{Examples}} \\ 
	\midrule  \midrule %\hline
        \textbf{Public} & Access is not restricted and is subject to open records requests  & Student directory information, employee’s business contact info \\
	\midrule  \midrule %\hline
        \multicolumn{3}{c}{ {\large {\textbf{Protected Data} } } } \\ 
	\midrule  \midrule %\hline
        \textbf{Restricted} & Used for UH business only; will not be distributed to external parties; released externally only under the terms of a written MOA or contract & Student contact information, UH ID number \\
	\midrule  
        \textbf{Sensitive} & Data subject to privacy considerations  & Date of birth, job applicant records, salary/payroll information, most student information \\
	\midrule  
        \textbf{Regulated} & Inadvertent disclosure or inappropriate access requires a breach notification by law or is subject to financial fines & FN or first initial/LN in combination with SSN, driver license number, or bank information; credit card, HIPAA, or financial aid information \\            
    \bottomrule
      \end{tabular}%
    }
  \end{table}
\end{frame}  
	%% \begin{columns}
	%% \begin{column}{0.46\textwidth}
	%% 	\begin{block}{}
	%% 	\begin{itemize}
	%% 		\item Quad Data Rate (QDR)\\InfiniBand{\regtrademark} (IB)   
	%% 			\begin{itemize}
	%% 				\item 40 Gbit
	%% 				\item Older compute nodes
	%% 				\item low latency ($\approx1.3\mu$s)
	%% 				\item non-blocking
	%% 			\end{itemize}
	%% 			~\\
	%% 		\item 25/100 Gbit Ethernet
	%% 			\begin{itemize}
	%% 				\item Newer compute nodes
	%% 				\item Nodes connected @ 25~Gbit
	%% 				\item non-blocking
	%% 			\end{itemize}
	%%         \end{itemize}
        %%         \end{block}
	%% \end{column}
	%% \begin{column}{0.46\textwidth}
	%% 	\begin{block}{External Networks}
	%% 	\begin{itemize}
	%% 		\item 100 Gbit SciDMZ
	%% 			\begin{itemize}
	%% 				\item Login \& compute nodes\\connected via a firewall
	%% 				\item DTNs are directly connected
	%% 			\end{itemize}
	%% 	\end{itemize}
        %%         \end{block}
	%% \end{column}
	%% \end{columns}

>>>>

\begin{frame}
  \frametitle{What is data governance}
  %        \begin{definition}\footnotesize
  %          Data governance is a data management concept concerning the capability that enables an organization to ensure that high data quality exists throughout the complete lifecycle of the data. The key focus areas of data governance include availability, usability, consistency, data integrity and data security and includes establishing processes to ensure effective data management throughout the enterprise such as accountability for the adverse effects of poor data quality and ensuring that the data which an enterprise has can be used by the entire organization.
  %        \footnote[1,frame]{\tiny \href{https://en.wikipedia.org/wiki/Data\_governance}{https://en.wikipedia.org/wiki/Data\_governance}}
  %        \end{definition}
  \begin{itemize}
  \item Defines how data is collected, stored, and used
  \item Defines who can access data, when, and under what conditions
  \item Establishes decision rights
  \item Establishes clear lines of accountability
  \item Gives a voice to all appropriate parties
  \item Provides a mechanism for conflict resolutions involving data
  \end{itemize}
\end{frame}

@@

\subsection{Data Classifications @ UH}
\begin{frame}
  \frametitle{Data Classifications @ UH}
  \vspace{-5pt}
  \makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%
      \begin{tabular}{l||p{6cm}||p{6cm}}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
	\toprule                                                                    
        \thead{\large\textbf{Category}} & \thead{\large\textbf{Definition}} & \thead{\large\textbf{Examples}} \\ 
	\midrule  \midrule %\hline
        \textbf{Public} & Access is not restricted and is subject to open records requests  & Student directory information, employee’s business contact info \\
	\midrule  \midrule %\hline
        \multicolumn{3}{c}{ {\large {\textbf{Protected Data} } } } \\ 
	\midrule  \midrule %\hline
        \textbf{Restricted} & Used for UH business only; will not be distributed to external parties; released externally only under the terms of a written MOA or contract & Student contact information, UH ID number \\
	\midrule  
        \textbf{Sensitive} & Data subject to privacy considerations  & Date of birth, job applicant records, salary/payroll information, most student information \\
	\midrule  
        \textbf{Regulated} & Inadvertent disclosure or inappropriate access requires a breach notification by law or is subject to financial fines & FN or first initial/LN in combination with SSN, driver license number, or bank information; credit card, HIPAA, or financial aid information \\            
    \bottomrule
      \end{tabular}%
    }    }
  \vspace{-5pt}
  \begin{block}{Protected Data}
    Collecting, managing, sharing or using  data that can be classified in a protected data category the Data Governance Process (DGP) is required 
  \end{block}
\end{frame}

\section{Regulations}

\begin{frame}
  \frametitle{Regulations}
\begin{block}{}
  The following lists of regulations are not exahustive lists that may apply to your data at the university (personal \& research).
  It is important that you know and understand what regulations the data you are working with is subject to.

\end{block}
\end{frame}

\subsection{Personally Identifiable Information (PII)  \& Financial Regulations}
\begin{frame}
  \frametitle{Regulations}
  \begin{block}{Personally Identifiable Information (PII)  \& Financial Regulations}
    \begin{itemize}
    \item \href{https://studentprivacy.ed.gov/ferpa-regulations}{Family Educational Rights and Privacy Act (FERPA)} [UH Policy \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ap\&policyChapter=7\&policyNumber=022\&menuView=closed}{AP 7.022}]
      \begin{itemize}
      \item Federal law that protects the privacy of student education records
      \end{itemize}

    \item Higher Education Act (HEA)
      \begin{itemize}
      \item Federal law that protects the federal financial aid information
      \end{itemize}

    \item \href{https://www.ftc.gov/tips-advice/business-center/privacy-and-security/gramm-leach-bliley-act}{Gramm-Leach-Bliley Act (GLBA)}
      \begin{itemize}
      \item Federal law that requires finanical institutions to explain how they share \& protect customer's data
      \end{itemize}

    \item \href{https://gdpr-info.eu/}{General Data Protection Regulation (GDPR)}
      \begin{itemize}
      \item A European Union (EU) consumer protection law that applies to companies collecting PII as part of delivering goods and services
      \end{itemize}

    \item \href{Health Insurance Portability and Accountability Act (https://www.hhs.gov/hipaa/for-professionals/security/laws-regulations/index.html}{HIPPA}) [UH Policy \href{https://www.hawaii.edu/policy/index.php?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=217\&menuView=closed}{EP 2.217}]
      \begin{itemize}
      \item Federal law that protects the privacy of health information
        \item \href{https://www.hawaii.edu/infosec/hipaa/}{HIPPA @ UH}
      \end{itemize}
    \end{itemize}  
  \end{block}
\end{frame}

\subsection{Federal Regulations}
\begin{frame}
  \frametitle{Regulations}
  \vspace{-5pt}
  \begin{block}{Federal Regulations}
    \begin{itemize}
    \item \href{https://csrc.nist.gov/publications/detail/sp/800-171/rev-1/final}{National Institute of Standards and Technology Special Programs (NIST) 800-171}
      \begin{itemize}
      \item Federal Department of Defense (DoD) standards aimed at safeguarding Controlled Unclassified Information (CUI)
      \item May apply to grants from DoD and possibly other federal agencies
      \end{itemize}

    \item \href{https://www.hsdl.org/?abstract\&did=461297}{National Industrial Security Program [DoD Directive 5220.22-M]}
      \begin{itemize}
      \item Classified data subject to regulation
      \end{itemize}

    \item \href{https://www.pmddtc.state.gov/ddtc_public?id=ddtc_public_portal_itar_landing\#tab-itar}{Export Control \& International Traffic in Arms Regulations (ITAR)}
      \begin{itemize}
      \item Federal regulations that impose access, dissemination or participation restrictions on the use and/or transfer of commodities, technical data, or the provision of services subject to United States (US) export controls for reasons of national security, foreign policy, anti-terrorism or non-proliferation
      \end{itemize}

    \item \href{https://www.bis.doc.gov/index.php/regulations/export-administration-regulations-ear}{Export Administration Regulations (EAR)}
      \begin{itemize}
      \item EAR govern whether a person may export a thing from the U.S., reexport the thing from a foreign country, or transfer a thing from one person to another in a foreign country. The EAR apply to physical things (sometimes referred to as "commodities") as well as technology and software.\footnote{\label{EAR on Wikipedia}\tiny\url{https://en.wikipedia.org/wiki/Export_Administration_Regulations}} 
      \end{itemize}
    \end{itemize}
\end{block}
\end{frame}

\subsection{State Regulations}
\begin{frame}
  \frametitle{Regulations}
  \vspace{-5pt}
  \begin{block}{State Regulations}
    \begin{itemize}
    \item \href{https://www.capitol.hawaii.gov/hrscurrent/Vol11_Ch0476-0490/HRS0487N/HRS_0487N-.htm}{{\hawaii} Revised Statues (HRS) 487N}
      \begin{itemize}
      \item State law that defines the breach notification to the legislature
      \item Examples: First name or First initial and Last name in combination with
        \begin{itemize}
        \item Social Security Number (SSN)
        \item Driver license or State ID \#
        \item Person's finanical account information
          \end{itemize}
      \end{itemize}

    \item \href{https://www.capitol.hawaii.gov/hrscurrent/Vol02_Ch0046-0115/HRS0092F/HRS_0092F-.htm}{Uniform Information Practices Act (UIPA)[HRS Chapter 92F]}
      \begin{itemize}
      \item Governs open records requests
      \end{itemize}
    \end{itemize}
\end{block}
\end{frame}

\section{UH Data Related Policies \& Procedures}
\begin{frame}
  \frametitle{UH Data Related Policies \& Procedures}
  \vspace{-7pt}
\makebox[\linewidth][c]{
    \resizebox{\textwidth}{!}{%                                                                                                                                                                                                                                                       
      \begin{tabular}{l||l}
      %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\                                                                                                                                                                                                       
        \toprule
        \thead{\large\textbf{Policy}} & \thead{\large\textbf{Description}} \\
        \midrule  \midrule %\hline
        \multicolumn{2}{c}{ {\large {\textbf{Administrative Procedure} } } } \\  
        \midrule \midrule
        \textbf{AP2.215} & Mandatory Training \& Continuing Education Requirements \\
        \midrule
        \textbf{AP7.022} & FERPA \\
        \midrule \midrule
        \multicolumn{2}{c}{ {\large {\textbf{Executive Policy} } } } \\  
        \midrule \midrule
        \href{https://www.hawaii.edu/policy/?action=viewPolicy\&policySection=ep\&policyChapter=2\&policyNumber=210\&menuView=closed}{\textbf{EP2.210}} & Use and Management of Information Technology Resources \\
        \midrule
        \href{}{\textbf{EP2.213}} & System and Campus Wide Electronic Channels for Communicating with Students\\
        \midrule        
        \textbf{EP2.214} & Data Classification Categories \& Information Security Guidelines \\
        \midrule
        \textbf{EP2.215} & Institutional Data Governance \\
        \midrule
        \textbf{EP2.216} & Institutional Records Management \& Electronic Approvals/Signatures (\textit{Pending Approval}) \\
        \midrule
        \textbf{EP2.217} & HIPPA (\textit{To be Revised}) \\
        \midrule
        \textbf{EP2.218} & Online Approvals of Internal University Transactions\\
        \midrule
        \textbf{EP2.2xx} & Student Online Data Protection Requirements (\textit{Draft}) \\
        \midrule
        \textbf{EP2.215} & Institutional Data Governance \\
        \midrule
        \textbf{EP8.200} & Policy on Contracts \& Signing Authority \\
        \bottomrule
      \end{tabular}%
      }
}
\vspace{-5pt}

\end{frame}

  %% \item General Data Protection Regulation (GDPR)
  %%   \begin{itemize}
  %%   \item A European Union (EU) consumer protection law that applies to companies collecting personally identifiable information (PII) as part of delivering goods and services
  %%   \end{itemize}

  %% \item General Data Protection Regulation (GDPR)
  %%   \begin{itemize}
  %%   \item A European Union (EU) consumer protection law that applies to companies collecting personally identifiable information (PII) as part of delivering goods and services
  %%   \end{itemize}

  %% \item General Data Protection Regulation (GDPR)
  %%   \begin{itemize}
  %%   \item A European Union (EU) consumer protection law that applies to companies collecting personally identifiable information (PII) as part of delivering goods and services
  %%   \end{itemize}

  %% \item General Data Protection Regulation (GDPR)
  %%   \begin{itemize}
  %%   \item A European Union (EU) consumer protection law that applies to companies collecting personally identifiable information (PII) as part of delivering goods and services
  %%   \end{itemize}

  %% \end{itemize}

  %% \begin{table}
  %%   \centering
  %%   \resizebox{\textwidth}{!}{%
  %%     \begin{tabular}{l||p{6cm}||p{6cm}}
  %%     %  \multicolumn{8}{c}{ {\large {\textbf{UH-HPC Resource Summary} } } } \\ 
  %%       \toprule                                                                    
  %%       \thead{\large\textbf{Regulation}} & \thead{\large\textbf{Description}} & \thead{\large\textbf{}} \\ 
  %%       \midrule  \midrule %\hline
  %%       \textbf{Public} & Access is not restricted and is subject to open records requests  & Student directory information, employee’s business contact info \\
  %%       \midrule  \midrule %\hline
  %%       \multicolumn{3}{c}{ {\large {\textbf{Protected Data} } } } \\ 
  %%       \midrule  \midrule %\hline
  %%       \textbf{Restricted} & Used for UH business only; will not be distributed to external parties; released externally only under the terms of a written MOA or contract & Student contact information, UH ID number \\
  %%       \midrule  
  %%       \textbf{Sensitive} & Data subject to privacy considerations  & Date of birth, job applicant records, salary/payroll information, most student information \\
  %%       \midrule  
  %%       \textbf{Regulated} & Inadvertent disclosure or inappropriate access requires a breach notification by law or is subject to financial fines & FN or first initial/LN in combination with SSN, driver license number, or bank information; credit card, HIPAA, or financial aid information \\            
  %%   \bottomrule
  %%     \end{tabular}%
  %%   }
  %% \end{table}

%% \begin{columns}
	%% \begin{column}{0.46\textwidth}
	%% 	\begin{block}{}
	%% 	\begin{itemize}
	%% 		\item Quad Data Rate (QDR)\\InfiniBand{\regtrademark} (IB)   
	%% 			\begin{itemize}
	%% 				\item 40 Gbit
	%% 				\item Older compute nodes
	%% 				\item low latency ($\approx1.3\mu$s)
	%% 				\item non-blocking
	%% 			\end{itemize}
	%% 			~\\
	%% 		\item 25/100 Gbit Ethernet
	%% 			\begin{itemize}
	%% 				\item Newer compute nodes
	%% 				\item Nodes connected @ 25~Gbit
	%% 				\item non-blocking
	%% 			\end{itemize}
	%%         \end{itemize}
        %%         \end{block}
	%% \end{column}
	%% \begin{column}{0.46\textwidth}
	%% 	\begin{block}{External Networks}
	%% 	\begin{itemize}
	%% 		\item 100 Gbit SciDMZ
	%% 			\begin{itemize}
	%% 				\item Login \& compute nodes\\connected via a firewall
	%% 				\item DTNs are directly connected
	%% 			\end{itemize}
	%% 	\end{itemize}
        %%         \end{block}
	%% \end{column}
	%% \end{columns}
